
\phantomsection
\addcontentsline{toc}{chapter}{\bf ABSTRACT}

\begin{center}
    \large{\bf ABSTRACT}
\end{center}

AIT Match is a dating platform created exclusively for students at the Asian Institute of Technology (AIT), offering a balanced approach between social and academic life within the university. The platform is designed to foster meaningful connections by leveraging both personal and academic information to create a tailored dating experience. Users can only register with a valid AIT email, ensuring that the platform remains a secure and trusted space for students.

Key features of AIT Match include personalized profile creation, where profiles are displayed based on personal characteristics and academic background, and robust preference filters, allowing users to search for matches by personality traits such as age, gender, MBTI type, interests, and relationship preferences, as well as academic information like schools, programs, and degrees. Additionally, real-time messaging is enabled exclusively between matched users, promoting communication only after mutual interest has been established.

AIT Match also includes an admin and reporting system, where users can report any inappropriate behavior to our admin team. This feature ensures that any issues are addressed promptly, maintaining a safe and respectful environment for all users.

By integrating academic and personal interests, AIT Match provides a platform that aligns with the values and community spirit of AIT. This application serves as a unique and focused alternative to traditional dating apps by prioritizing academic context and personal connections within the university environment.
