\chapter{INTRODUCTION} 

\section{Background of the Study}
    In the digital age, online platforms have become a widely accepted medium for forming relationships, particularly among university students who are adept with technology. However, existing dating applications cater to a broad demographic, making them less tailored to the unique social and academic dynamics of university life. These generalized platforms often lack the contextual depth necessary to foster meaningful connections based on shared academic experiences, social interests, or professional aspirations.

    At the Asian Institute of Technology (AIT), students come from diverse cultural and academic backgrounds, creating an environment rich in opportunities for meaningful connections. However, the demands of academic life, coupled with the challenges of navigating a multicultural environment, often make it difficult for students to engage in social and romantic relationships. Many students express a desire to connect with peers who share similar academic goals, career aspirations, and social interests, yet there is no existing platform specifically designed to facilitate this within the university context.
    
    AIT Match is designed to address this gap by offering a university-exclusive dating platform where AIT students can connect based on shared academic and social interests. The platform focuses on providing a secure and trusted environment where users can form meaningful connections reflective of their academic and personal lives. Unlike generic dating apps, AIT Match is uniquely positioned to leverage the academic and social context of university life, fostering deeper relationships while ensuring authenticity through a verified university email registration process. This approach ensures that the platform remains exclusive to the AIT community, enhancing trust and connection within the student body.

\newpage
\section{Statement of the Problem}
    In today's digital landscape, many platforms are designed to facilitate social and romantic connections. However, these platforms target a broad audience and do not meet the unique needs of university students, particularly those seeking meaningful relationships grounded in their academic environment. For students at the Asian Institute of Technology (AIT), the absence of a platform that integrates both academic and social aspects presents several challenges:
    \sloppy
    \begin{enumerate}
        \item \textbf{Limited Focus on Academic Connections:} Existing platforms often emphasize quick, surface-level interactions, lacking features to connect users based on their academic programs, courses, or career aspirations, making it harder to find peers with aligned academic interests.
        
        \item \textbf{Inadequate Filtering Options:} Without filters for academic backgrounds, students have fewer opportunities to connect with peers in their field of study. The ability to search by academic criteria such as degree program, faculty, or school is crucial but often restricted or unavailable.
        
        \item \textbf{Lack of University-Specific Features:} Current platforms do not offer features tailored to the university experience, leaving students without a secure environment to connect based on both academic and personal interests.
        
        \item \textbf{Time Constraints of Master's and Doctoral Students:} Postgraduate students, particularly those pursuing master’s and doctoral degrees, often struggle to engage in social or romantic activities due to their demanding schedules. A platform that integrates academic and personal preferences can simplify this process, allowing them to find like-minded peers more efficiently.
    \end{enumerate}
    
    The lack of a platform that balances academic and social interests within a university-specific environment creates a significant gap for AIT students. This project aims to fill that gap by developing a platform that integrates academic information with personal preferences, offering a balanced approach to dating and social interaction within the AIT community.

\newpage
\section{Objectives}
    The primary objective of this project is to develop a dating platform exclusively for students at the Asian Institute of Technology (AIT), with a focus on enhancing both social and academic engagement. The specific objectives of the project are as follows:
    \sloppy
    \begin{enumerate}
        \item \textbf{Create a University-Exclusive Dating Platform:}
        Provide a dating platform specifically for AIT students, fostering connections within the university community.
        \item \textbf{Ensure User Safety and Trust}:
        Implement a university email verification process to ensure that all users are part of the AIT community, fostering a safer and more trusted environment for interaction.
        \item \textbf{Build a Secure and User-Friendly Platform}:
        Develop an intuitive and secure platform that enhances user experience, ensuring ease of use while maintaining a high level of data security and privacy.
        \item \textbf{Develop a Customized Matching System}:
        Build a matching system that allows users to filter potential matches by academic and personal preferences, such as degree, program, interests, and personality traits.
        \item \textbf{Enhance Social Engagement}:
        Encourage students to build relationships through shared social interests, facilitating meaningful connections beyond academic settings.
        \item \textbf{Enhance Academic Engagement}:
        Promote interactions based on academic backgrounds, helping students connect through shared academic interests, programs, and schools.
    \end{enumerate}


\newpage
\section{Target User}
The primary target users of AIT Match are students from the Asian Institute of Technology (AIT), encompassing all academic disciplines. AIT students come from a diverse array of cultural, professional, and educational backgrounds, each pursuing rigorous academic programs that require significant time and dedication. Given these academic demands, many students find it challenging to engage in social activities or form meaningful connections within their community. AIT Match aims to address this gap by providing a platform that allows students to connect with peers who share not only social interests but also academic and professional goals. This approach ensures that users can find others who understand the unique pressures and opportunities associated with university life.

By catering to the entire AIT student body, AIT Match fosters a sense of inclusivity and belonging within the community. The platform allows students to filter potential matches based on shared academic fields, extracurricular activities, and personal interests, thereby facilitating connections that are both relevant and meaningful. Whether students are pursuing degrees in engineering, management, science, or any other discipline, AIT Match creates a space where academic and social engagement can intersect. The platform’s focus on shared academic experiences and extracurricular involvement ensures that it serves as a tool for building lasting relationships within the AIT community, enriching the student experience across all programs.


\newpage
\section{Scope of the Project}
The scope of this thesis encompasses the development of a web-based platform designed to facilitate user interaction through a set of well-defined functionalities. The platform is structured around user and administrative roles, with the following key features:

\begin{itemize} 

    \item \textbf{Development of a Web-based Platform:}
    The project involves the creation of a web-based platform that enables users to access its features via a web browser on multiple devices.
    
    \item \textbf{Data Management through SQL Database Architecture:}  
    The platform utilizes an SQL-based database architecture to efficiently manage and store user data, ensuring scalability, reliability, and data integrity.
    
    \item \textbf{User Functionalities:}  
    Users can act both as general users and as administrators. The functionalities provided to general users include the following:
    
    \begin{itemize}
        \item \textbf{Landing Page:}  
        The landing page presents a navigation bar that provides access to the homepage, information about the platform, contact details, user login, and sign-up options.

        \item \textbf{User Authentication:}  
        The platform supports secure user authentication through registration with a university email address and password. Users can reset their password via email if needed.
    
        \item \textbf{Main Page:}  
        Upon successful login, users are directed to the main page. The navigation bar on this page includes links to key features such as profile creation, preference management, matches, and messages.  The homepage provides a searchable list of profiles, with sorting options such as alphabetical (A-Z or Z-A) and random profile display.
    
        \item \textbf{Profile Management:}  
        Upon initial registration, users are required to create a personal profile. This profile contains both personal and academic information, including first name, last name, username, email address, date of birth, gender, MBTI type, interests, relationship preferences, and a profile picture URL. Additionally, users can manage academic details such as degrees, schools, programs, and educational background. Users can view their own profiles as well as those of other users, with the option to edit their information at any time.
    
        \item \textbf{Preference Management:}  
        Users have the ability to set preferences to filter displayed profiles based on a range of criteria, including age range, preferred gender, interests, relationship preferences, MBTI type, degrees, schools, programs, and username. Filtered profiles are prominently displayed on the homepage, tailored to each user's preferences.
    
        \item \textbf{Matching System:}
        The platform includes a robust matching system that allows users to express interest in connecting with others. When a user sends a match request, the recipient is notified in real time through a notification icon displayed on the navigation bar. If the recipient accepts the request, both profiles appear in the “Matches” section, enabling the users to communicate with each other. Pending match requests are displayed on a dedicated “Match Requests” page, allowing users to manage incoming connection requests easily.
    
        \item \textbf{Messaging Functionality:}  
        The messaging feature is available exclusively to users who have successfully matched. Messages between users are displayed in the "Messages" section, along with a timestamp indicating when each message was sent.

        \item \textbf{Report System:}
        Users can report inappropriate behavior on profiles to the AIT Match admin. The report status is updated in real time, and once the admin reviews the report, the status is changed accordingly. This system ensures prompt handling of issues to maintain a safe and respectful environment on the platform.
    \end{itemize}

    \item \textbf{Admin Functionalities:}
    The system includes a single admin, designated by the developer, with distinct capabilities separate from regular users. The admin has access to the following functionalities:

    \begin{itemize}
        \item \textbf{Profile Deletion:} The admin has the authority to view and delete user profiles. If a user engages in inappropriate or harmful behavior, their account may be banned from the platform.

        \item \textbf{Report Management:} Only the admin has access to view reports submitted by users, which are displayed on the admin dashboard. The admin can review these reports and take appropriate action, such as removing the reported user from the platform to ensure the safety of all users. The status of each report is visible to the reporting user after it has been reviewed. Once reviewed, the admin can choose to delete or retain the report, while users do not have permission to delete it.
    \end{itemize}
 \end{itemize}

%\ section{Organization of the Study}
%   Start your paragraph here.